Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-08 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Updating...

In order to understand this question, it is instructive to consider
the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis,}
\end{cases}
\end{equation}
where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
is a sub-event space. $\mu_{0}$ is not induced by the Born rule as
a whole, but is consistent with the Born rule on $\events_{0}$ and
some other proper sub-event spaces. Formally, given a quantum IVPM~$\bar{\mu}$,
the \emph{core} relative to a sub-event space~$\events'\subseteq\events$
as follow.\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, it could increase the difficulty to explain classical IVPMs
because we might need to explain the meaning of the Born rule for
classical probability measures...}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
where $\circ$ denote function composition, and $\iota_{\infty}$
is defined in Eq.~(\ref{eq:iota_infty}).

@@

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty
core relative to $\events_{0}$ which is commutative. In general,
a commutative sub-event space reduces quantum IVPMs to classical IVPMs.
We haven't found any classical IVPM has an empty core, and Shapley
proved that a good enough classical IVPM always has a non-empty core.

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item For all commuting $P_{0},P_{1}\in\events$, 
\[
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
\]
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

>>>>

In order to understand this question, it is instructive to consider
the 2-dimensional quantum probability measure~$\mu_{0}:\events\rightarrow[0,1]$
defined as follow:
\begin{equation}
\mu_{0}(P)=\begin{cases}
\mu_{\ket{\ps}}^{\mathrm{B}}(P) & \textrm{, if }P\in\events_{0}\textrm{ ;}\\
\mu_{\ket{0}}^{\mathrm{B}}(P) & \textrm{, otherwis,}
\end{cases}
\end{equation}
where $\events_{0}=\left\{ \mathbb{0},\proj{\ps},\proj{\ms},\mathbb{1}\right\} $
is a sub-event space. $\mu_{0}$ is not induced by the Born rule as
a whole, but is consistent with the Born rule on $\events_{0}$ and
some other proper sub-event spaces. The similar phenomena happens
for IVPMs as well. Formally, given a quantum IVPM~$\bar{\mu}$, the
\emph{core} relative to a sub-event space~$\events'\subseteq\events$
is\footnote{\yutsung{I changed the definition of core to embedding the Born rule.
While this change might make it easier to explain the core of quantum
IVPMs, should we explain the meaning of the Born rule for classical
probability measures?}}
\begin{equation}
\mathrm{core}\left(\bar{\mu},\events'\right)=\set{\rho}{\forall P\in\events'.~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}\textrm{ .}
\end{equation}
The core of an interval-valued probability measure is the set of states
it approximates. For example, $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{0}\right)=\left\{ \proj{\ps}\right\} $,
$\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events_{1}\right)=\left\{ \proj{0}\right\} $
and $\mathrm{core}\left(\iota_{\infty}\circ\mu_{0},\events\right)=\emptyset$,
where $\circ$ denotes function composition, $\iota_{\infty}$ is
defined in Eq.~(\ref{eq:iota_infty}), and $\events_{1}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $.
That is, $\iota_{\infty}\circ\mu_{0}$ approximates $\proj{\ps}$
if we are only allowed to use $\events_{0}$ during the measurement,
approximates $\proj{0}$ if $\events_{1}$ is allowed, and approximates
nothing if every projector is allowed.

Notice that $\iota_{\infty}\circ\mu_{0}$ has a non-empty core relative
to $\events_{0}$ and $\events_{1}$ which are all commutative. In
general, a commutative sub-event space reduces quantum IVPMs to classical
IVPMs. If a classical IVPM satisfies a coherence condition, convexity,
it must approximate at least one infinitely-precise measure.

\begin{thm}[Shapley~\cite{Shapley1971,Grabisch2016}]\label{thm:Shapley}For
every interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$,
if the following conditions are true.
\begin{itemize}
\item $\events'$ is commutative, i.e., $\bar{\mu}$ is classical.
\item $\bar{\mu}$ is convex, i.e., for all commuting $P_{0},P_{1}\in\events$,
\[
\bar{\mu}\left(P_{0}\vee P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}
\]
where $P_{0}\vee P_{1}=P_{0}+P_{1}-P_{0}P_{1}$~\cite{Griffiths2003}.
\end{itemize}
Then, $\mathrm{core}\left(\bar{\mu},\events'\right)\ne\emptyset$.\end{thm}

@@
